How do school travel planning stakeholders frame active school travel in Ontario, Canada?

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.tex

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How do school travel planning stakeholders frame active school travel in Ontario, Canada?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\hypertarget{school-travel-planning-in-canada}{%
\subsection{1.1. School travel planning in
Canada}\label{school-travel-planning-in-canada}}

Walking and bicycling to school, commonly known as active school travel
or active school transportation (AST), has been declining in Canada and
North America for decades ({\textbf{???}}), with levels much lower than
other developed countries like The Netherlands ({\textbf{???}}) and
Japan ({\textbf{???}}). This trend has prompted a multi-sector response
to identify strategies to increase AST, the most popular of which is a
growing interest in school travel planning across Canada.

School travel planning (STP) is a ``school-specific'' intervention led
by a facilitator that brings together a committee of stakeholders from
diverse sectors including education, planning, transportation, and
public health ({\textbf{???}}). Parents and parent councils also
typically have a role in supporting or implementing STP. The
intervention encourages participation from the broader community and
collaboration between involved stakeholders, who contribute their
expertise to remove ``school-specific'' barriers to AST and to identify
strategies for promoting and encouraging AST. STP may also involve other
stakeholders including local advocacy groups or environmental
organizations who are familiar with the state of AST at the
community-level. Buliung et al.~({\textbf{???}}) piloted an STP
intervention at 12 schools in 4 Canadian provinces and reported that it
increased AST rates and led to a ``mobilization of diverse community
resources''. Since this seminal study, STP interventions have become
increasingly popular and common at schools across Canada and have even
attracted funding from provincial governments.

\hypertarget{correlates-of-active-school-travel}{%
\subsection{1.2. Correlates of active school
travel}\label{correlates-of-active-school-travel}}

Factors that influence AST are typically conceptualized according to the
socioecological model whereby children's travel behaviour is understood
within the context of their household, social, and built environments
(see {\textbf{???}}). At the individual level, older child age is often
associated with AST ({\textbf{???}}; {\textbf{???}}; {\textbf{???}}).
There is some evidence that gender is a determinant of AST
({\textbf{???}}; {\textbf{???}}), although this is not a strong or
consistent finding ({\textbf{???}}; {\textbf{???}}). Distance between
home and school is associated with AST ({\textbf{???}}; {\textbf{???}};
{\textbf{???}}; {\textbf{???}}) with less AST reported among children
who have to travel farther to school. Car ownership is an important
household-level influence on AST ({\textbf{???}}; {\textbf{???}};
{\textbf{???}}), as is household income ({\textbf{???}}). Parental
perceptions of the environment ({\textbf{???}}; {\textbf{???}}) and
children's skills ({\textbf{???}}) also influence whether they allow
their children to walk or cycle to school. Finally, many studies have
found that the quality of the built environment ({\textbf{???}};
{\textbf{???}}) and active travel infrastructure ({\textbf{???}})
facilitate AST. Concerns about traffic and strangers have been reported
by parents who drive their children to school ({\textbf{???}}). The
consensus is that all of these factors are interrelated and that
interventions ought to target multiple factors in order to increase
walking and bicycling levels to school.

\hypertarget{benefits-of-ast}{%
\subsection{1.3. Benefits of AST}\label{benefits-of-ast}}

The desire to increase AST is warranted - there is strong evidence that
children who walk and bicycle to school accrue physical and mental
health benefits. Many studies and reviews have focused on the
association between AST or CIM and physical activity (e.g.,
{\textbf{???}}; {\textbf{???}}; {\textbf{???}}), with findings
consistently demonstrating that children who travel by walking or
bicycling to school are more active than their peers who do not use
active travel. More recently, researchers have been exploring the link
between transport and children's wellbeing ({\textbf{???}};
{\textbf{???}}), which has relevant applications to the study of school
travel and satisfaction (see {\textbf{???}}). CIM is also important for
different domains of children's health and wellbeing ({\textbf{???}}).
It offers benefits such as increasing traffic and safety skills,
boosting spatial awareness when navigating public spaces, and providing
more opportunity for social interaction with peers ({\textbf{???}}).

\hypertarget{encouraging-adoption-of-active-school-travel}{%
\subsection{1.4. Encouraging adoption of active school
travel}\label{encouraging-adoption-of-active-school-travel}}

To increase rates of walking and bicycling independently to school,
Riazi et al.~({\textbf{???}}) state: ``it will be vital for
interventions to target modifiable factors, including children's and
parents' perceptions of their social environment.'' Parents play the
important role of ``gatekeeper'' by either granting or restricting CIM
licenses, meaning whether children can travel alone ({\textbf{???}}).
For this reason, stakeholders involved in STP produce information
targeted for both children and parents, and aim to involve the broader
community in their efforts to increase the number of children walking
and bicycling to school.

However, the ways in which interventions like STP are framed to their
target audience can ultimately influence how they are received and
whether they result in behaviour change. The correlates of AST are
important knowledge for policymakers because they identify points of
intervention and potential benefits that ought to be communicated to the
public encourage adoption of AST and to build support for new planning
paradigms. What is less clear is how CIM plays into the consideration of
policymakers when they act on the objective of increasing AST.

Any goals for AST, and also CIM, ought to be clearly articulated and
reflected in transportation plans and policies to guide initiatives.
Presently, however, there has been no study to date that explores how
Canadian municipalities and schools frame and discuss AST with the
public. Content analysis is one method to analyze how particular issues
are framed to groups of people, for instance parents or educators who
might be inclined to support AST. It attempts to understand how
information presented from a ``communicator'' leads the ``receiver'' to
a desired response ({\textbf{???}}). In a recent paper ({\textbf{???}}),
framing analysis was applied to review municipal policies addressing
climate change in four western Canadian cities. Natural language
processing (NLP) has also been used for a similar purpose to examine
content in general plans from Californian cities ({\textbf{???}}). The
way policy issues are framed is ultimately important to understand
because it plays a role in either altering or preserving the existing
social perceptions.

\hypertarget{study-aim}{%
\subsection{1.5. Study aim}\label{study-aim}}

In 2017, the provincial government of Ontario in Canada issued funding
to Green Communities Canada (GCC), a non-profit organization, to launch
the \emph{Ontario Active School Travel} (OAST) program. The program
provides funding for school and community-based initiatives and supports
stakeholders in municipalities across the province to implement STP and
other interventions aimed at increasing AST. As of 2021, OAST has funded
\emph{X} projects in Ontario. GCC continues has funded projects across
Ontario led by collaborative groups involving school boards, municipal
or regional governments, and regional transportation consortia. The
latter are dedicated transportation bodies that deliver efficient and
effective transportation services, which generally focus on providing
the school busing service to families in their associated region.

The aim of this paper is to analyze how AST is framed by STP
stakeholders in Ontario, Canada. We used text mining and topic modelling
to examine how local policy documents from Ontario municipalities and
school boards present and communicate the benefits and barriers of AST
and the solutions for improving AST. We compared the findings from these
documents to a selection of studies on AST and explored the extent to
which research findings have trickled down to inform policy and planning
for increasing AST.

\hypertarget{data}{%
\section{2. Data}\label{data}}

\hypertarget{data-retrieval}{%
\subsection{2.1. Data retrieval}\label{data-retrieval}}

\hypertarget{policy-documents}{%
\subsubsection{2.1.1. Policy documents}\label{policy-documents}}

We assembled a collection of publicly available documents that were
sourced online from the main stakeholder groups involved in STP
initiatives in Ontario: i) school boards (public and English-speaking
only); ii) municipal governments; and iii) transportation consortia.
Non-profit organizations, police services, and advocacy groups are other
stakeholders who may play a role in supporting AST and/or STP, but this
study does not include any documents from these groups because they are
not consistently participating in initiatives.

The search was guided first by a list of all English public school
boards across Ontario. The websites of each school board were manually
searched for pages related to school transportation or travel. Any pages
relevant to these topics were manually downloaded. Next, we collected
documents by searching municipal government and transportation consortia
websites. The latter were identified based on geographic area (i.e., the
municipalities and/or transportation consortia who are in the same
geographic area of each school board). Pages related to active or school
travel were manually downloaded. Webpages from STP stakeholder websites
were included in our analysis if they were easy to find. This primary
criteria was important since our analysis pertains to how such issues
are framed to the public. Thus, we included only webpages that were easy
to find, which we defined as requiring no more than 2-4 separate links
from the initial Google search.

@@

\hypertarget{academic-papers}{%
\subsubsection{2.2.1. Academic papers}\label{academic-papers}}

\hypertarget{data-cleaning}{%
\subsection{2.2. Data cleaning}\label{data-cleaning}}

@@

\hypertarget{methods}{%
\section{3. Methods}\label{methods}}

\hypertarget{natural-language-processing}{%
\subsection{3.1. Natural language
processing}\label{natural-language-processing}}

\hypertarget{reproducibility}{%
\subsection{3.2. Reproducibility}\label{reproducibility}}

@@

\hypertarget{results}{%
\section{4. Results}\label{results}}

\hypertarget{word-and-document-frequency}{%
\subsection{4.1. Word and document
frequency}\label{word-and-document-frequency}}

@@

\hypertarget{bigrams-and-concordances}{%
\subsection{4.2. Bigrams and
concordances}\label{bigrams-and-concordances}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{MunicipalTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(municipal_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{M_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(MunicipalTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
\NormalTok{municipal_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(M_it_train)}

\NormalTok{municipal_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(municipal_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
\NormalTok{municipal_vocab}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Number of docs: 28 
## 0 stopwords:  ... 
## ngram_min = 1; ngram_max = 1 
## Vocabulary: 
##            term term_count doc_count
##   1:        abc          5         1
##   2: accessible          5         5
##   3:     adding          5         3
##   4:   addition          5         3
##   5:       ages          5         4
##  ---                                
## 350:    cycling         78        22
## 351:       bike         87        15
## 352:    walking         90        25
## 353:     travel        126        20
## 354:     active        248        26
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ConsortiumTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(consortium_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{C_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(ConsortiumTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
\NormalTok{consortium_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(C_it_train)}

\NormalTok{consortium_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(consortium_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
\NormalTok{consortium_vocab}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Number of docs: 9 
## 0 stopwords:  ... 
## ngram_min = 1; ngram_max = 1 
## Vocabulary: 
##           term term_count doc_count
##   1:    around          5         4
##   2:    assist          5         2
##   3:    choice          5         3
##   4: classroom          5         1
##   5: committee          5         1
##  ---                               
## 124:  students         39         9
## 125:    travel         41         8
## 126:      walk         49         8
## 127:   walking         55         8
## 128:    active         67         7
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{SchoolTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(school_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{S_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(SchoolTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
\NormalTok{school_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(S_it_train)}

\NormalTok{school_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(school_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
\NormalTok{school_vocab}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Number of docs: 32 
## 0 stopwords:  ... 
## ngram_min = 1; ngram_max = 1 
## Vocabulary: 
##                term term_count doc_count
##   1:       academic          5         4
##   2: administration          5         4
##   3:      alternate          5         3
##   4:       assigned          5         2
##   5:         attend          5         5
##  ---                                    
## 264:        walking         57        17
## 265:    information         65        21
## 266:         travel        103        11
## 267:            bus        120        20
## 268:         active        124        13
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{PolicyTextDF <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{text =} \KeywordTok{sapply}\NormalTok{(policy_corpus, as.character), }\DataTypeTok{stringsAsFactors =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{P_it_train =}\StringTok{ }\KeywordTok{itoken}\NormalTok{(PolicyTextDF}\OperatorTok{$}\NormalTok{text, }\DataTypeTok{progressbar =} \OtherTok{FALSE}\NormalTok{)}
\NormalTok{policy_vocab =}\StringTok{ }\KeywordTok{create_vocabulary}\NormalTok{(P_it_train)}

\NormalTok{policy_vocab <-}\StringTok{ }\KeywordTok{prune_vocabulary}\NormalTok{(policy_vocab, }\DataTypeTok{term_count_min =} \DecValTok{5}\NormalTok{)}
\NormalTok{policy_vocab}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Number of docs: 69 
## 0 stopwords:  ... 
## ngram_min = 1; ngram_max = 1 
## Vocabulary: 
##           term term_count doc_count
##   1:       abc          5         1
##   2: according          5         4
##   3:  actively          5         4
##   4:  addition          5         3
##   5: addresses          5         3
##  ---                               
## 698:      walk        145        39
## 699:       bus        164        35
## 700:   walking        202        50
## 701:    travel        270        39
## 702:    active        439        46
\end{verbatim}

@@

\caption{Most common bigrams found in all of the policy documents (i.e., school board, municipality, and transportation consortia combined.}\label{fig:policy-visual}
\end{figure}

We combined all of the municipality, school board, and transportation
consortia documents into one ``policy'' corpora. This enabled us to
examine and visualize the most common bigrams found across all of the
STP material in Ontario. Figure \ref{fig:policy-visual} shows all of the
bigrams that occur more than 10 times in the corpora. In addition to the
common bigrams already identified above, we also found \emph{mental
health}, \emph{walk day}, and \emph{green communities} as common pairs
of consecutive words. Overall, policy documents from STP stakeholders
focus on four key areas: i) benefits or impacts of AST; ii) mechanisms
of intervention; iii) concerns or considerations; and iv) supports for
AST.

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggraph}\NormalTok{(academic_bigram_graph, }\DataTypeTok{layout =} \StringTok{"fr"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_edge_link}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{edge_alpha =}\NormalTok{ n), }\DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{,}
                 \DataTypeTok{arrow =}\NormalTok{ a, }\DataTypeTok{end_cap =} \KeywordTok{circle}\NormalTok{(.}\DecValTok{07}\NormalTok{, }\StringTok{'inches'}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_node_point}\NormalTok{(}\DataTypeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{4}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_node_text}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ name), }\DataTypeTok{repel =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{theme_void}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{AST-Framing-Ontario_files/figure-latex/unnamed-chunk-10-1.pdf}

We interpreted the most common bigrams from the policy corpora (see
Figure \ref{fig:policy-visual}), which includes all documents from
municipalities, transportation consortia, and school boards, as the main
ideas that STP stakeholders are focusing on and communicating to the
public about AST. We used the \texttt{kwic} function from the R
\emph{quanteda} package to identify and better understand identify the
context of these key themes.

>>>>

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How do school travel planning stakeholders frame active school travel in Ontario, Canada?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

Walking and bicycling to school, commonly known as active school travel
(AST), has been declining in Canada and North America for decades
({\textbf{???}}), with levels much lower than other developed countries
like The Netherlands ({\textbf{???}}) and Japan ({\textbf{???}}). In
response to this trend, school travel planning has become a popular
intervention across Canada that has resulted in mixed success with some
schools reporting an increase in AST (e.g., {\textbf{???}}; Mammen et
al., 2014), while others did not observe a change in behaviour
(Buttazzoni et al., 2019) or needed more time and resources to be
effective ({\textbf{???}}).

School travel planning (STP) is a ``school-specific'' intervention led
by a facilitator that brings together a committee of stakeholders from
diverse sectors including education, planning, transportation, and
public health to develop action plans ({\textbf{???}}). This five-step
process involves identifying barriers to AST based on the local context
and implementing approaches or activities that alleviate concerns and
encourage AST ({\textbf{???}}). STP facilitators and committee members
generally intervene at the school through a range of activities such as
educational strategies, in-person events or programs, improvements to
the school site, and enforcement (Mammen et al., 2014).

How STP is framed to a target audience may influence how this
intervention is received and whether it encourages the audience to
support it or participate. In particular, STP stakeholders make choices
about the points of intervention and potential benefits that ought to be
communicated to the public to facilitate adoption of AST. Educational
strategies, which account for approximately one quarter of STP
strategies implemented at Canadian schools (Mammen et al., 2014), need
to effectively engage multiple audiences -- parents, students,
politicians -- on the issue, challenges, and benefits of AST.
Promotional materials, therefore, should reflect current knowledge from
research about school travel and the built environment, as well as local
content specific to factors that influence travel decisions for parents,
in order to effectively engage the public in advocating for improving
AST or to expose parents and the community to essential information that
may prompt behaviour change.

On the one hand, parents have been found to express different
understandings, nomenclature, and conceptualizations than planners of
the factors that influence school travel (Buliung et al., 2021).
However, it is unknown to what degree there is concurrence between STP
materials presented to the public and the literature on school travel
and parental perceptions, and how the complexity of the AST issue is
presented to the public.

The aim of this paper is to fill this research gap by analyzing how AST
is framed by STP stakeholders in Ontario, Canada. We used text mining
and topic modelling to examine how local policy documents from Ontario
municipalities and school boards present and communicate the benefits
and barriers of AST and the solutions for improving AST. We compared the
findings from these documents to a selection of studies on AST and
explored the extent to which there is concurrence between research
findings to date and promotional materials shared with the public to
increase AST.

\hypertarget{literature-review}{%
\section{2. Literature Review}\label{literature-review}}

\hypertarget{data}{%
\section{3. Data}\label{data}}

\hypertarget{data-retrieval}{%
\subsection{3.1. Data retrieval}\label{data-retrieval}}

\hypertarget{policy-documents}{%
\subsubsection{3.1.1. Policy documents}\label{policy-documents}}

We assembled a collection of publicly available documents that were
sourced online from the main stakeholder groups involved in STP
initiatives in Ontario: i) school boards (public and English-speaking
only); ii) municipal governments; and iii) transportation consortia.
Non-profit organizations, police services, and advocacy groups are other
stakeholders who may play a role in supporting AST and/or STP, but this
study does not include any documents from these groups because they are
not consistently participating in all initiatives.

The search was guided first by a list of all English public school
boards across Ontario. The websites of each school board were manually
searched for pages related to school transportation or travel. Any pages
relevant to these topics were manually downloaded. Next, we collected
documents by searching municipal government and transportation consortia
websites. The latter were identified based on geographic area (i.e., the
municipalities and/or transportation consortia that are in the same
geographic area of each school board). Pages related to active or school
travel were manually downloaded. Webpages from STP stakeholder websites
were included in our analysis if they were easy to find. This primary
criteria was important since our analysis pertains to how such issues
are framed to the public. Thus, we included only webpages that were easy
to find, which we defined as requiring no more than 2-4 separate links
from the initial Google search.

@@

\hypertarget{academic-papers}{%
\subsubsection{3.2.1. Academic papers}\label{academic-papers}}

\textbf{To be completed by Dr.~Paez}

\hypertarget{data-cleaning}{%
\subsection{3.2. Data cleaning}\label{data-cleaning}}

@@

\hypertarget{methods}{%
\section{4. Methods}\label{methods}}

\hypertarget{framing-analysis}{%
\subsection{4.1. Framing analysis}\label{framing-analysis}}

Issues that pertain to public health or wellbeing are often presented to
the public through particular frames to influence perceptions or
behaviours. Gamson and Modigliani ({\textbf{???}}) conceptualize a frame
as a ``central organizing idea or story line that provides meaning'' to
a particular phenomenon. A frame can enable individuals ``to locate,
perceive, identify, and label'' information pertaining to various
dimensions of an issue (Goffman, 1974). Scholars in the field of
political communications have proposed that communicators, such as the
media or an institution, construct the narrative of a frame for policy
positions or public issues in order to activate or restrict a particular
response in the intended audience (Pan and Kosicki, 1993). Framing can
be used to position existing solutions as suitable to address particular
issues (Mah et al., 2014), which may prevent the public from being aware
of other policy approaches that challenge the status quo to bring about
more radical change. The way policy issues are framed is ultimately
important to understand because it plays a role in either altering or
preserving the existing social perceptions.

Framing of issues is an important step in developing health policy. An
obvious example over the past decade is the framing of climate change as
a public health issue (e.g., @ depouxCommunicatingClimateChange2017;
Maibach et al., 2010; Weathers and Kendall, 2016) to increase public
engagement and reception of the issue. Transport planners also use
different frames to guide the extent to which transport policies can be
adapted to address climate change. In a recent paper ({\textbf{???}}),
framing analysis was applied to review the representation of issues such
as mobility and social exclusion in municipal policies from four western
Canadian cities under the current circumstances of climate change. The
authors found four primary frames: ``The Growing City'', ``If You Build
It, They Will Come'', ``Better City for All'', and a ``the Resilient
City''. Each frame presented the nature, opportunities, and challenges
of climate change in different ways which set the stage for the types of
mitigation and adaptation strategies that cities were proposing to
address this issue.

Given the range of factors at multiple levels of the socioecological
model that influence school travel, it is important to understand how
walking and bicycling to school are framed to the public. Is active
school travel framed as a public health or environmental issue? Is it
framed as both? Do proposed solutions to increase AST focus primarily on
the intrapersonal and interpersonal factors, meaning that behaviour
change must ultimately result from different decisions made by the
individual or the household? Or is the decline in AST framed as an issue
that must be addressed through changes in the built environment? These
are the types of questions that we aim to answer in this paper. To our
knowledge, this topic has not be addressed in the school travel
literature to date.

\hypertarget{topic-modelling}{%
\subsection{4.2. Topic modelling}\label{topic-modelling}}

The topic modelling analysis was conducted in R. We primarily used the
following packages: \texttt{topicmodels} ({\textbf{???}}),
\texttt{word2vec} ({\textbf{???}}), and \texttt{wordcloud}
({\textbf{???}}) to examine content in the documents that were sourced
for this project. These packages have functions for determining the
frequency of specific words in each document, relationships (e.g., pairs
of adjacent terms) and correlations between words, and estimating Latent
Dirichlet allocation (LDA) models to classify documents according to the
topics that are contained within them. We describe in the section below
how we used these functions to produce our results.

\hypertarget{reproducibility}{%
\subsection{4.3. Reproducibility}\label{reproducibility}}

@@

\hypertarget{results}{%
\section{5. Results}\label{results}}

\hypertarget{word-and-document-frequency}{%
\subsection{5.1. Word and document
frequency}\label{word-and-document-frequency}}

@@

\hypertarget{bigrams-and-concordances}{%
\subsection{5.2. Bigrams and
concordances}\label{bigrams-and-concordances}}

@@

@@

\caption{Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined).}\label{fig:policy-visual}
\end{figure}

We then combined all municipality, school board, and transportation
consortia documents into one ``policy'' corpora. This enabled us to
examine and visualize the most common bigrams found across all of the
STP material in Ontario that was collected for this study. Figure
\ref{fig:policy-visual} shows all of the bigrams that occur more than 10
times in the corpora. In addition to the common bigrams already
identified above, we also found \emph{mental health}, \emph{walk day},
and \emph{green communities} as common pairs of consecutive words.
Overall, policy documents from STP stakeholders seem to focus on four
key areas: i) benefits or impacts of AST; ii) mechanisms of
intervention; iii) concerns or considerations; and iv) supports for AST.

@@

{\centering \includegraphics[width=1\linewidth]{AST-Framing-Ontario_files/figure-latex/academic-visual-1}

\caption{Most common bigrams found in the academic papers.}\label{fig:academic-visual}
\end{figure}

We interpreted the most common bigrams from the policy corpora (see
Figure \ref{fig:policy-visual}), which includes all documents from
municipalities, transportation consortia, and school boards, as the main
ideas that STP stakeholders are focusing on and communicating to the
public about AST. We then used the \texttt{kwic} function from the R
\emph{quanteda} package to identify and better understand the context of
these key themes. Table \ref{tab:policy-concordance} presents examples
of the key themes that were extracted from select policy documents to
demonstrate how the most common bigrams are communicated to the public.

\begin{table}
\centering
\begin{tabular}[t]{>{}l|l|>{\raggedright\arraybackslash}p{30em}}
\hline
Terms & Stakeholder & Context\\
\hline
\textbf{Air Quality} & School Board & Active transportation [...] improves air quality.\\
\hline
\textbf{Benefit} & Municipality & Stronger bones and muscles, improved self-esteem and sense of well-being while reducing stress and risk of chronic disease all benefit those who use active transportation.\\
\hline
\textbf{Bus} & School Board & While taking part in a walking school bus, your child will enjoy seeing friends on the way to school. They will be active more often. This is also a great opportunity for your child to socialize with school friends in a monitored and safe way where they can practice social distancing, modelled by a leader.\\
\hline
\textbf{Community} & School Board & Engage community stakeholders (school boards, municipalities, police, public health professionals, parents/guardians, administrators, educators and children) to work together to identify and to solve their school travel needs.\\
\hline
\textbf{Emissions} & Consortia & An active school commute also reduces congestion in school zones and contributes to reducing greenhouse gas emissions – it’s a win-win for everyone!\\
\hline
\textbf{Health} & Municipality & Active School Travel allows school-aged children the chance to participate in moderate to intense physical activity. This is linked with lower body mass index and improved cardiovascular health.\\
\hline
\textbf{Lanes} & Municipality & We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.\\
\hline
\textbf{Mental Health} & Municipality & ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.\\
\hline
\textbf{Physical Health} & Municipality & Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.\\
\hline
\end{tabular}
\end{table}

\hypertarget{topic-modelling-1}{%
\subsection{5.3. Topic modelling}\label{topic-modelling-1}}

\begin{verbatim}
## Warning: `guides(<scale> = FALSE)` is deprecated. Please use `guides(<scale> =
## "none")` instead.
\end{verbatim}
